A Comparison of Parallel Graph Processing Benchmarks

### 2017-02-17 papers/publication/paper-pollard.tex
more related edits (mainly rewording)

Other related work includes that of \cite{Satish:2014:NavigatingGraph}, which analyzes performance of several systems on datasets on the order of $30$ billion edges and \cite{Lu:2014:ExperimentalEval} which uses six real-world datasets and focuses on the vertex-centric programming model.

Our approach differs from the previously mentioned appproaches because it focuses on the depth of analysis rather than the breadth via diversity of datasets or graph processing systems. We analyze  power and energy consumption in addition to details such as the number of iterations or the time to construct the data structures. Additionally, our approach requires little knowledge of the inner workings of each system; the data are collected using either sampling of model specific registers (for power) or parsing log files (for timing).

>>>>

Satish et al.~\cite{Satish:2014:NavigatingGraph} analyze the performance of several systems on datasets on the order of $30$ billion edges and \cite{Lu:2014:ExperimentalEval} uses six real-world datasets and focuses on the vertex-centric programming model.

Unlike these approaches, we focus on the \emph{depth} of analysis rather than the breadth via diversity of datasets or graph processing systems. We analyze  power and energy consumption in addition to details such as the number of iterations or the time to construct the data structures. Moreover, our approach requires little knowledge of the inner workings of each system; the data are collected using either hardware counter sampling of model-specific registers (for power) or through parsing log files (for timing).
